\section{Dynamic Traffic Light Adjustment (Type 1)}

\subsection*{1. Main Goal}

The main goal of this task is to optimize real-time urban traffic flow by dynamically adjusting traffic light durations based on sensor data. The system detects when a road is experiencing significantly more traffic than crossing roads and modifies green/red light timings accordingly to reduce congestion.

\subsection*{2. Section Goals}

This section focuses on designing a system that automatically monitors traffic patterns through event-based sensors and adjusts traffic lights without human intervention. All actions taken must be logged for traceability, and a daily report is generated to summarize traffic conditions and interventions. The real-time traffic status is also made available to citizens through an application, while only traffic managers have access to daily reports.

\subsection*{3. Requirement Analysis}

\subsubsection*{3.1 Relevant Human and Non-Human Actors}

\textbf{Human Actors:}
\begin{itemize}
    \item Traffic Manager – accesses daily reports summarizing actions taken by the system.
    \item Citizen – views real-time traffic conditions through the application.
\end{itemize}

\textbf{Non-Human Actors:}
\begin{itemize}
    \item Sensor System – provides real-time traffic data through an event-based infrastructure.
    \item Analyzer – processes traffic data and detects imbalances.
    \item Traffic Light System – receives and executes updated timing instructions.
    \item Logger – records each adjustment with metadata for traceability.
    \item Application – provides a user interface for citizens and traffic managers.
\end{itemize}

\subsubsection*{3.2 Use Cases}

\begin{itemize}
    \item Detect high-traffic roads in real time based on sensor data.
    \item Adjust green and red light durations to relieve congestion.
    \item Log each adjustment for traceability.
    \item Generate and provide daily reports for traffic managers.
    \item Display real-time traffic flow data to users via the application.
\end{itemize}

\subsubsection*{3.3 Domain Assumptions}

\begin{enumerate}
    \item Traffic sensors send reliable and periodic data via a message bus.
    \item The Analyzer is able to interpret traffic data within a few seconds.
    \item Traffic Light System supports dynamic configuration of light durations.
    \item Each intersection and road is uniquely identified in the system.
    \item Logger guarantees persistent and tamper-proof logging of actions.
    \item Traffic managers have secure access to daily reports.
    \item Citizens have access to the application interface to monitor real-time traffic.
\end{enumerate}

\subsubsection*{3.4 Requirements}

\paragraph{3.4.1 Functional Requirements}

\begin{itemize}
    \item \textbf{FR1.1:} The system shall receive real-time traffic data from sensors at regular intervals (e.g., every 30 seconds).
    \item \textbf{FR1.2:} The Analyzer shall process incoming data to identify roads with significant congestion.
    \item \textbf{FR1.3:} The system shall dynamically adjust the green/red duration of traffic lights to relieve congestion.
    \item \textbf{FR1.4:} Each light adjustment shall be recorded by the Logger with a timestamp, location, and duration changes.
    \item \textbf{FR1.5:} The system shall generate a daily report summarizing traffic flow and Type 1 actions.
    \item \textbf{FR1.6:} The daily report shall be accessible only by authorized traffic managers.
    \item \textbf{FR1.7:} The real-time traffic conditions shall be viewable by all users via the application.
\end{itemize}

\paragraph{3.4.2 Non-Functional Requirements}

\begin{itemize}
    \item The system shall respond to new sensor data and adjust light durations within 5 seconds.
    \item The system shall be available 24/7 with at least 99\% uptime.
    \item The Logger shall ensure secure, persistent, and traceable storage of all records.
    \item The daily report shall be generated and made available to traffic managers by 00:00 each day.
    \item The system shall be scalable to manage hundreds of intersections across the city.
    \item The application interface shall be responsive and usable on both desktop and mobile devices.
    \item Access to the daily report shall be role-restricted to authorized traffic managers only.
\end{itemize}